---
title: 'Project: Web Pages with Less than 100 Pageviews since 3/1/2019'
author: "Office of Marketing and Brand Management"
date: "6/19/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

### Description

The purpose of this project is to provide information to the web team in the Office of Marketing and Brand Management to assist them in determining which web pages have been viewed fewer than 100 times since March 1, 2019. This report documents the process and results of Step 1, determining whether we can merge the web page content data provided by Robin McGlauflin, Web Design Manager in Information Technology Services at USM, with the web traffic data retreived from Google Analytics.   

```{r}
library(knitr)
library(reactable)
library(tidyverse)
library(stringr)
library(kableExtra)
```


```{r get GA data}
# library(googleAnalyticsR)
# library(googleAuthR)
# ga_auth()
# start_date <- "2019-03-02"
# end_date <-  Sys.Date()
# my_accounts <- ga_account_list()
# View(my_accounts)
# ga_id_2 <- 50446675
# campaign_filter <- dim_filter(dimension="pagePath",operator="REGEXP",expressions="/eng/")
# my_filter_clause <- filter_clause_ga4(list(campaign_filter))
# 
# GA_thisWk_I <- google_analytics(ga_id_2, date_range = c(start_date, end_date),
#                                 metrics = c("pageviews"),
#                                 dimensions = c("pageTitle", "pagePath"),
#                                 dim_filters = my_filter_clause,
#                                 anti_sample = TRUE
#                                 )
# 
# IncludeInternal <- GA_thisWk_I %>% arrange(desc(pageviews))
# write.csv(IncludeInternal, "C:/Users/christine.iyer/Box/WebVisits/Data/Eng_IncludeInternal_Path.csv", row.names = T)
# dim(IncludeInternal)
```

```{r data}
IncludeInternal <- read.csv("C:/Users/christine.iyer/Box/WebVisits/Data/Eng_IncludeInternal_Path.csv", header = T, stringsAsFactors = F)

English <- read.csv("C:/Users/christine.iyer/Box/WebVisits/Data/EngExample.csv", header = T, stringsAsFactors = F)
```

```{r rename url for common fields}
English <- English %>% rename(URL = URL.ALIAS, Page_Title = PAGE.TITLE)
IncludeInternal <- IncludeInternal %>% rename(URL = pagePath, Page_Title = pageTitle)
```

```{r inspect}

#ENG_IncludeInternal <- IncludeInternal %>% filter(URL == str_subset(URL,"^/eng/*")) %>% arrange(Page_Title) %>% select(Page_Title, URL, pageviews)
English <- English %>% arrange(Page_Title)%>% select(Page_Title, URL)

```


```{r join}
new <- merge(IncludeInternal,English, by="URL") 

kable(new %>% 
        arrange(pageviews) %>% 
        mutate(Row_Number = seq.int(nrow(new))) %>% 
        select(Row_Number, pageviews,Page_Title.y,URL) %>% 
        filter(pageviews < 100), caption = "Findings: Test Merge CM Data: English Sites with fewer than 100 pageviews since 3/1/2019 ",) %>% 
  kable_styling("latex" , latex_options = c("repeat_header", "scale_down")) %>% 
  landscape()
```


__Process__

1. Import CM data and and rename URL and Page Title fields

1. Import GA data. Fields required - "pagePath", "pageTitle", and "pageviews". Querying data via api is possible. The process is in hidden code in this report.

1. Merge the 2 reports with "merge" function and select appropriate fields and then arrange pageviews in ascending order. 

 
### Results

* The test merge using the English Dept pages provided by Robin was successful. 

* Approximately 40 of the 90 English subsites have gotten less than 100 pageviews since early March, 2019. 

\href{https://www.wrike.com/open.htm?id=524341284}{{\color{blue}{\underline{Wrike Project Details}}}}

\href{https://github.com/edithbird/web-visits}{{\color{blue}{\underline{Github Repository}}}}

__Box File: WebVisits__
